{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-21 documents/acknowledgement.tex
text

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.

Dr. Dainis' videos on microbiological technique were also useful.

Thanks to the professors at York and beyond for returning my emails.

Thanks to L.H. for wisdom regarding this project.

Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.

Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

@@

>>>>

Thanks to (Dr. ) Peter Barfuss for spending time reviewing early drafts.

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools.

Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiological technique were also particularly useful.

Thanks to all the professors at York and beyond for returning my emails and checking their biofridges for phages.

GThanks to L.H. for wisdom regarding this project; and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.

Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

\rule{\linewidth}{0.2pt}

The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also unavailable via email.

\rule{\linewidth}{0.2pt}

The authors acknowledge the IT.IS foundation for doing the same, but actually replying to emails.

\rule{\linewidth}{0.2pt}

@@

{\Large <3}

\end{document}

### 2020-09-21 documents/distribution.tex
text

Let us therefore re-examine the reason why.

@@

@@

Charge \footnotemark

>>>>

Let us therefore re-examine the microwave spectrum. Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.

@@

Lorentzian

@@

Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, and T4. however, a few influzena proteins have been found to have anomalous secondary structure charge.

Because CryoEM uses charged particles, it is technically feasible to determine the net charge distribution in the whole virus using an ingenious \cite{Identification2018} technique. However, this has not yet been implemented in any

\footnotemark

### 2020-09-21 documents/paper.tex
Wrote a better abstract
text

@@

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.} 
%
, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.

>>>>

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
	\caption{\\ The {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}

\end{figure}

@@

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.} 
%
, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.

### 2020-09-21 documents/pseudo_soliton.tex
text

Assuming that a torso is about 10 penetration depths in radius, this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).

>>>>

At 9 GHz, assuming that a torso is about 10 penetration depths in radius, implementing this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).

### 2020-09-21 documents/supplemental.tex
text

>>>>

This has nothing to do with , but it's an amusing parlor trick that I accidentally ran into while trying to carbothermally reduce copper oxide powder. It led me to the SiC susceptor resonator, so it wasn't a total waste.

Add a thimblefull of fine copper powder to the bottom of a mason jar. Cover the mouth with a layer of Kapton tape. Next, inject pure argon gas for a few minutes, then seal the tape fully.

Put the whole shebang in a friend's microwave oven.

Wait patiently. There will be a sizable bang and a terrific plasma.

My hypothesis is that this is due to the higher ionization energy of Ar. Air seems to slowly leak in, decreasing the
